The role of lithic bipolar technology in Western Iberia’s Upper Paleolithic: the case of Vale Boi (southern Portugal)

### 2018-12-03 analysis/paper/paper.Rmd
bar.plot.mean

area <- mean..bar.plot(techno_data, "Chronology", "Area", "RawMaterial")
thickness <- mean..bar.plot(techno_data, "Chronology", "Thickness", "RawMaterial")

>>>>

area <- bar.plot.mean(techno_data, "Chronology", "Area", "RawMaterial")
thickness <- bar.plot.mean(techno_data, "Chronology", "Thickness", "RawMaterial")
